19Q2

### 2019-10-29 19Q2.Rmd
update Rmd

```{r}
dataframe <- crispr_fus
grouping <- c("FusionPair", "Drug", "Drug_FusionPair")

count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
count_category <- count_n %>% count(Drug_FusionPair) %>% filter(n == 2)
# keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
# dataframe <- filter(dataframe, Drug_FusionPair %in% keep)
# dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
# signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
```

@@

  if(!is.na(str_match(string = tolower(feature), pattern = "crispr")) & is.na(str_match(string = tolower(feature), pattern = "prot"))) {
    print("Making CRISPR mutation status grid and annotation dataframes.")
    signif_df <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene))
    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0)
    signif_grid <- signif_grid[match(g2p_gene_order, signif_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)

@@

      signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
      signif_grid_annot[signif_grid_annot == "resistance"] <- "X"
      signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
      print("Done.")
    }
  }
  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
    print("Making fusions grid and annotation dataframes.")
    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]

@@

    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
    print("Done.")
  }
  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(1.5, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)

  print("Making heatmap object.")
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = na_color,
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  if(color == "darkorchid4") {
                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.18 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
                  }
                  if(color == "steelblue4") {
                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.12 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
                  }
                  if(color == "darkgreen") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
                      radius <- height*0.16
                    }
                    else { radius <- width*0.18 }
                  }
                  if(color == "turquoise4") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) {
                      radius <- height*0.16
                    }
                    else { radius <- width*0.18 }
                  grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.07, gp = gpar(fontsize = 17))

                  if(signif_grid_annot[i, j] == "O") {
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                  if(signif_grid_annot[i, j] == "X") {
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                  }
                  if(signif_grid_annot[i, j] == "resistance") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                  }
                  if(signif_grid_annot[i, j] == "both") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                }

@@

**10/23 STOPPED HERE: Was fixing annotation dot sizes on heatmaps**

@@

ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                              ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                               ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)                                ", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
png(filename = "./plots/manuscript/all_prot_heatmap.png", width = 14, height = 5, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

```{r fus_heatmaps, eval=FALSE}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

@@

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.4, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

@@

@@

Spearman correlations for gene expression and copy number:
```{r spear_calc, warning=FALSE, eval=FALSE}
# CRISPR
crispr_spear_cn <- transform(crispr %>% group_by(Gene) %>% drop_na(CN) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
c("white", "deepskyblue4")
crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .after = "Gene")
saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor.rds")

crispr_spear_ge <- transform(crispr %>% group_by(Gene) %>% drop_na(TPM) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .after = "Gene")
saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor.rds")

# CCLE
ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
ccle_filt <- unfactorize(ccle_filt)
ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
ccle_ge_res$InG2P <- ifelse(ccle_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
ccle_ge_res$Dataset <- "CCLE"

ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
ccle_cn_res$InG2P <- ifelse(ccle_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
ccle_cn_res$Dataset <- "CCLE"

# CTRP
ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
ctrp_filt <- unfactorize(ctrp_filt)
ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
ctrp_ge_res$InG2P <- ifelse(ctrp_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
ctrp_ge_res$Dataset <- "CTRP"

ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
ctrp_cn_res$InG2P <- ifelse(ctrp_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
ctrp_cn_res$Dataset <- "CTRP"

# GDSC
gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
gdsc_filt <- unfactorize(gdsc_filt)
gdsc_ge_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
gdsc_ge_res$InG2P <- ifelse(gdsc_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
gdsc_ge_res$Dataset <- "GDSC"

gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
gdsc_cn_res$InG2P <- ifelse(gdsc_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
gdsc_cn_res$Dataset <- "GDSC"

@@

# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
```

```{r}
    signif_df <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene))
    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0)
    signif_grid <- signif_grid[match(g2p_gene_order, signif_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)

>>>>

@@

  if(!is.na(str_match(string = tolower(feature), pattern = "crispr")) & is.na(str_match(string = tolower(feature), pattern = "prot|fus"))) {
    print("Making CRISPR mutation status grid and annotation dataframes.")
    signif_df <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene))
    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0)
    signif_grid <- signif_grid[match(g2p_gene_order, signif_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)

@@

      signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
      signif_grid_annot[signif_grid_annot == "resistance"] <- "X"
      signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
      print("Done.")
    }
  }
  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
    if(is.na(str_match(string = tolower(feature), pattern = "crispr"))) {
      print("Making fusions grid and annotation dataframes.")
      signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
      signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
      signif_grid <- signif_grid[complete.cases(signif_grid), ]

@@

      signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
      signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
      signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
      signif_grid_annot[signif_grid_annot == "No"] <- ""
      signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
      print("Done.")
    }
    if(!is.na(str_match(string = tolower(feature), pattern = "crispr"))) {
      print("Making CRISPR fusions grid and annotation dataframes.")
      signif_grid <- dcast(signif_df, FusionPair ~ Drug_Gene, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)

      signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
      signif_grid_annot[signif_grid_annot == "No"] <- ""
      signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
      print("Done.")
    }
  }
  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(1.5, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)

  print("Making heatmap object.")
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = na_color,
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  if(color == "darkorchid4") {
                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
                  }
                  if(color == "steelblue4") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.20 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
                    else { radius <- width*0.18 }
                  }
                  if(color == "darkgreen") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.16 }
                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.3 }
                    else { radius <- width*0.17 }
                  }
                  if(color == "turquoise4") {
                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) { radius <- height*0.16 }
                    else { radius <- width*0.18 }
                  }

                  grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.065, gp = gpar(fontsize = 17))

                  if(signif_grid_annot[i, j] == "O") {
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                  if(signif_grid_annot[i, j] == "X") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                  }
                  if(signif_grid_annot[i, j] == "resistance") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                  }
                  if(signif_grid_annot[i, j] == "both") {
                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                })

@@

@@

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")

png(filename = "./plots/manuscript/all_prot_heatmap.png", width = 14, height = 5, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

**10/25 Need to fix InG2P annots on CTRP data**

```{r fus_heatmaps, eval=FALSE}
ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/crispr_fus_heatmap.png", width = 3, height = 3, units = "in", res = 500)
draw(ht_crispr, heatmap_legend_side = "top")
dev.off()

ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

@@

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "CRISPR -log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Fusion Pairs")

png(filename = "./plots/manuscript/all_fus_heatmap.png", width = 15, height = 2.4, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

**10/23 MADE PLOTS UP TO HERE**

@@

**10/23 NEED TO RUN LINEAGE PLOTS**

@@

Spearman correlations for gene expression and copy number:
```{r spear_calc, warning=FALSE, eval=FALSE}
# CRISPR
crispr_spear_cn <- crispr %>% group_by(Gene) %>% drop_na(CN) %>%
  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
            CN_p_log10 = -log10(CN_p),
            InG2P = "No",
            Dataset = "CRISPR",
            Metric = "Copy Number")
crispr_spear_cn <- transform(crispr_spear_cn, Gene = reorder(Gene, CN_r))
crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .before = "Gene")
Drug_Gene <- with(crispr_spear_cn, paste0(Drug, "_", Gene))
crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene = Drug_Gene, .before = "Drug")
saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor.rds")

crispr_spear_ge <- crispr %>% group_by(Gene) %>% drop_na(TPM) %>%
  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
            GE_p_log10 = -log10(GE_p),
            InG2P = "No",
            Dataset = "CRISPR",
            Metric = "Gene Expression")
crispr_spear_ge <- transform(crispr_spear_ge, Gene = reorder(Gene, GE_r))
crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .before = "Gene")
Drug_Gene <- with(crispr_spear_ge, paste0(Drug, "_", Gene))
crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene = Drug_Gene, .before = "Drug")
saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor.rds")

# CCLE
ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
ccle_filt <- unfactorize(ccle_filt)
ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
            GE_p_log10 = -log10(GE_p))
ccle_ge_res$InG2P <- ifelse(ccle_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
ccle_ge_res$Dataset <- "CCLE"

ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
            CN_p_log10 = -log10(CN_p))
ccle_cn_res$InG2P <- ifelse(ccle_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
ccle_cn_res$Dataset <- "CCLE"

# CTRP
ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
ctrp_filt <- unfactorize(ctrp_filt)
ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value,
            GE_p_log10 = -log10(GE_p))
ctrp_ge_res$InG2P <- ifelse(ctrp_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
ctrp_ge_res$Dataset <- "CTRP"

ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
            CN_p_log10 = -log10(CN_p))
ctrp_cn_res$InG2P <- ifelse(ctrp_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
ctrp_cn_res$Dataset <- "CTRP"

# GDSC
gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
gdsc_filt <- unfactorize(gdsc_filt)
gdsc_ge_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value,
            GE_p_log10 = -log10(GE_p))
gdsc_ge_res$InG2P <- ifelse(gdsc_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
gdsc_ge_res$Dataset <- "GDSC"

gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
            CN_p_log10 = -log10(CN_p))
gdsc_cn_res$InG2P <- ifelse(gdsc_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
gdsc_cn_res$Dataset <- "GDSC"

@@

ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
```

**10/28 FIX CRISPR PART OF corr_heatmap_function**
